\documentclass[10pt]{article}
\usepackage{color}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath}
\pagestyle{plain}


%opening
\title{Term Project Defense}
\author{Chris Card \& Marshall Sweatt\\
CSCI 598A: Human Centered Robotics\\
Dr. Hao Zhang\\
Department of Electrical Engineering and Computer Science\\
Colorado School of Mines}

\begin{document}
\maketitle
\newpage

\begin{abstract}
{\color{red} An abstract of 200 to 300 words summarizing your term projects and findings.} 
We have decided to implement and evaluate gmapping on a Turtlebot.  In order to navigate the Turtlebot through CSM, a controller package was created in a custom built framework.  We integrated the Kinect and Gmapping packages into our framework.  The 3${rd}$ floor of old Brown Building was mapped through RC control and then autonomously navigated using Monte Carlo localization approach package named ``amcl.''
\end{abstract}

\section{Introduction}
{\color{red} An introduction describing
your term project, including the task
and formulation of research problems, a brief description of your methods, and structure of your final paper.}

\section{Approach}
{\color{red}A detailed description of your approach, with enough information to understand
and enable someone to recreate your system.}

\section{Experiments}
{\color{red}Experimental results plus an explanation and discussion of the results, such as in what situations your system can obtain the best performance, when it fails, the efficiency of your program, etc}


\section{Conclusion}
{\color{red}A conclusion and future work section that summaries your term project, point out future work you believe would improve your implementation, and any other insightful observations you’d like to make.}

\appendix
\textbf{Workload Report}
{\color{red} If it’s a team work, a workload report in Appendix (agreed upon by all team members, which states what each team member did on this project in detail, along with a percentage breakdown (totaling 100\%).}

\end{document}